\documentclass[]{resume-openfont}

\pagestyle{fancy}
\resetHeaderAndFooter

%--------------------------------------------------------------
% Convenience command - make it easy to fill template

% Create job position command. Parameters: company, position, location, when
\newcommand{\resumeHeading}[4]{\runsubsection{\uppercase{#1}}\descript{ | #2}\hfill\location{#3 | #4}\fakeNewLine}

% Create education heading. Parameters: Name, degree, location, when
\newcommand{\educationHeading}[4]{\runsubsection{#1}\hspace*{\fill}  \location{#3 | #4}\\
\descript{#2}\fakeNewLine}

% Create project heading. Parameters: Name, link, Tech stack
\newcommand{\projectHeading}[3]{\Project{#1}{#2}
\descript{#3}\\}

\newcommand{\projectHeadingWithDate}[4]{\Project{#1}{#2}
\descript{#3 | #4}\\}

% Parameters: courses
\newcommand{\courseWork}[1]{\textbf{Coursework:} #1}

% Parameters: courses
\newcommand{\teacherAssistant}[1]{\textbf{Teacher Assistant (TA):} #1}
 
%--------------------------------------------------------------
\begin{document}

%--------------------------------------------------------------
%     Profile
%--------------------------------------------------------------
\newcommand{\yourName}{PRAVINKANNA PARTHIBAN}
\newcommand{\yourRole}{Senior Software Engineer}
% How you want it to show up on the resume
% \newcommand{\yourWebsite}{website.com}
% vs how you want it to show up. If it's the same you can just replace "\yourWebsiteLink" with "yourWebsite"
\newcommand{\yourWebsiteLink}{https://website.com}
\newcommand{\yourEmail}{pravinkannap@gmail.com}
\newcommand{\yourPhone}{+919843638308}
\newcommand{\githubUserName}{pravinkanna}
\newcommand{\linkedInUserName}{pravinkanna}

\begin{center}
    \Huge \scshape \latoRegular{\yourName} \\ \vspace{1pt}
    \LARGE {\yourRole} \\ \vspace{6pt}
    \small \href{mailto:\yourEmail}{\underline{\yourEmail}}  $|$  \yourPhone $|$ 
    \href{https://github.com/\githubUserName}{\underline{github/\githubUserName}} $|$ 
    \href{https://www.linkedin.com/in/\linkedInUserName}{\underline{linkedin/\linkedInUserName}}
    
    % $|$ \href{\yourWebsiteLink}{\underline{\yourWebsite}}
\end{center}

%--------------------------------------------------------------
%     Skills
%--------------------------------------------------------------
\section{Skills}
\begin{skillList}
   \doubleItem{Languages \& Frameworks:}{Golang, Node.js, TypeScript/JavaScript, Python, NestJS, Express.js}%
   {}{}%
    \\
    \doubleItem{Database \& Messaging:}{PostgreSQL, MongoDB, Elasticsearch, Redis, Kafka, RabbitMQ}%
    {}{}%
    \\
    \doubleItem{Tools:}{GCP, Docker, Kubernetes, GitHub Actions, Prometheus, Grafana, Sentry, Git, Postman, IMAP}%
    {}{}%
\end{skillList}

\sectionsep


%--------------------------------------------------------------
%     Experience
%--------------------------------------------------------------
\section{Work Experience}
\resumeHeading{Vumonic Datalabs}{Senior Software Engineer}{Bengaluru, India}{Jan 2021 – Present}
\begin{bullets}
    \item Led the engineering team of 3 members by directly managing frontend and DevOps engineers while reporting to the CEO and establishing engineering standards across the organization.
    \item Designed and implemented a email monitoring system for 3 million users, reducing processing delay from 8 hours to zero by utilizing the IMAP IDLE protocol to maintain persistent TCP connections for real-time email updates.
    \item Led the successful migration of 80 TiB storage, 30 services, and 5 databases from Oracle Cloud to GCP with zero downtime, using open-source tools like Rclone for data transfer.
    \item Reduced production errors by 70\% by migrating legacy Node.js v10 services to Go 1.23, implementing strict type checking, comprehensive error handling, and Sentry monitoring for automated error tracking and alerts
    \item Architected and built new SaaS product called Inboox.AI in 5 months, implementing subscription management, OAuth2 authentication, text search engine, and automated billing using Golang, Node.js, Typesense, and Stripe.
    \item Reduced deployment time by more than 90\% and eliminated manual interventions by implementing Docker containerization and Kubernetes automation for 30+ microservices.
    \item Achieved zero developer dependency for marketing reports by developing a self-service KPI dashboard that automated report generation.
\end{bullets}
\sectionsep

\resumeHeading{PretVA}{Fullstack Developer Intern}{Remote}{Oct 2020 - Dec 2020}
\begin{bullets}
    \item Improved user communication efficiency by developing a real-time chat system using WebSocket, facilitating seamless interactions between buyers and suppliers.
    \item Enhanced user experience and design consistency by revamping the web application, adhering to provided prototypes and UX guidelines.
\end{bullets}
\sectionsep

\resumeHeading{T4TEQ Software Solutions}{Tutor}{Tamil Nadu, India}{Jan 2020 - Aug 2020}
\begin{bullets}
    \item Taught programming fundamentals to 50+ students with a 95\% course completion rate, covering Python, data structures, and basic algorithms.
\end{bullets}
\sectionsep

%--------------------------------------------------------------
%     Projects
%--------------------------------------------------------------
\section{Projects \& Hackathons}

\projectHeading{Codeaholic}{https://github.com/Pravinkanna/codeaholic-v2}{React, Node.js, ExpressJS, MongoDB, Redis}
 An online IDE for writing, running, and sharing code, using an open-source code executor to run code securely within Docker containers. This resulted in 300+ weekly page views and 500+ code submissions.
\sectionsep

\projectHeading{Horsey}{https://devfolio.co/projects/horsey-find-the-best-rewards-on-web-c09f}{React, Node.js, ExpressJS, Solidity}
A web3 app built during the ETHIndia 2022 Hackathon to enable protocols to distribute rewards, such as airdrops and allowlists, to targeted user groups that completed proof-of-humanity verification via Worldcoin.
\sectionsep
  

%--------------------------------------------------------------
%     Education
%--------------------------------------------------------------
\section{Education}
% Put school first and degree second if your school is reputable
\educationHeading{B.Sc. Computer Science}{Bishop Heber College}{Tamil Nadu, India}{Jun 2021} \\
\courseWork{Data Structures and Algorithms, Object Oriented System Design, Operating Systems, Database Design, Database-Driven Web Design, Software Engineering, and Computer Networking.}
\sectionsep

\end{document}